Circumnuclear Media and Accetion Rates of Quiescent Supermassive Black Holes

### 2015-02-20 ms.tex
More

\begin{figure*}
\includegraphics[width=\textwidth]{miller.pdf}
\caption{\label{fig:miller} $\epsilon_X \Mdot c^2/L_{edd}$ predicted
  from our models compared to $L_X/L_{Edd}$ values (red stars) and
  upper limits (red triangles) from \citet{Miller+15}.
  $\epsilon_X=10^{-4}$ in the left-hand panel and $\epsilon_X=0.1
  \frac{\Mdot}{0.01 \MdotEdd}$ in the right-hand panel. The green and
  blue curves represent our predictions for core ($\Gamma=0.1$, blue)
  and cusp ($\Gamma=0.8$) galaxies respectively. They are calculated
  from equation~\eqref{eq:mdot_analytic}. The wind heating
  parameter, $v_w$ and mass return parameter, $\eta$, calculated for
  the average star formation histories in \citet{MosterNaab+:2013a}
  (the black lines in Figures~\ref{fig:vwSources}
  and~\ref{fig:eta}). Note that the star formation histories in
  \citet{MosterNaab+:2013a} are in terms of halo mass and for each
  $\Mbh$ we assign the halo mass, whose star formation history would
  produce a bulge consistent with the $\Mbh-M_{\rm bulge}$
  relationship from \citet{McConnellMa:2013a}.  We also show upper
  limits $\epsilon_X \Mdot c^2/L_{edd}$ from thermal stability
  (purple) and Ia supernovae (orange).}
\end{figure*}

>>>>

\begin{figure*}
\includegraphics[width=\textwidth]{miller.pdf}
\caption{\label{fig:miller} $\epsilon_X \Mdot c^2/L_{edd}$ predicted
  from our models compared to $L_X/L_{Edd}$ values (red stars) and
  upper limits (red triangles) from \citet{Miller+15}.
  $\epsilon_X=10^{-4}$ in the left-hand panel and $\epsilon_X=0.1
  \frac{\Mdot}{0.01 \MdotEdd}$ in the right-hand panel. The green and
  blue curves represent our predictions for core ($\Gamma=0.1$, blue)
  and cusp ($\Gamma=0.8$) galaxies respectively. They are calculated
  from equation~\eqref{eq:mdot_analytic}, with the wind heating
  parameter, $v_w$ and mass return parameter, $\eta$, corresponding to
  the the average star formation histories in
  \citet{MosterNaab+:2013a} (the black lines in
  Figures~\ref{fig:vwSources} and~\ref{fig:eta}). Note that the star
  formation histories in \citet{MosterNaab+:2013a} are in terms of
  halo mass and for each $\Mbh$ we assign the halo mass, whose star
  formation history would produce a bulge consistent with the
  $\Mbh-M_{\rm bulge}$ relationship from \citet{McConnellMa:2013a}.
  We also show upper limits $\epsilon_X \Mdot c^2/L_{edd}$ from
  thermal stability (purple) and Ia supernovae (orange).}
\end{figure*}
